README

### 2023-08-07 README.Rmd
modified readme with paper title
minor modification
version before first co-author review round

@@

-   .Rprofile - defines paths and activates `renv`, options for Posit R package manager
-   tables - main and supplementary tables (R objects and .docx format)
-   figures - main and supplementary figures (R objects and .docx format)
-   renv/renv.lock - `renv` directories to manage R dependencies and versions used in this simulation

@@

```{r}
fs::dir_tree(recurse = 1)
```

>>>>

# smdi: An R package to perform structural missing data investigations on partially observed confounders in real-world evidence studies

@@

-   .Rprofile - defines paths and activates `renv`, options for Posit R package manager
-   manuscript - manuscript, bibliography, cover letter and meta files to render to .docx format
-   tables - main and supplementary tables (R objects and .docx format)
-   figures - main and supplementary figures (R objects and .docx format)
-   renv/renv.lock - `renv` directories to manage R dependencies and versions used in this simulation

@@

```{r, echo = FALSE}
fs::dir_tree(recurse = 1)
```
